Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
codebook visualization section improved

\subsection{Codebook}
We can present the most typical patterns (Figure \ref{fig:codes1}). 
Then, LLE\footnote{implementation: 
\url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}} 
\cite{Roweis2000}? (Figure \ref{fig:lle}). 
Then, the graph on variance. (Figure \ref{fig:code_var}).

>>>>

\subsection{Codebook}
Visualizing codewords in a meaningful way is always a challenge, 
even if we have only a one or two hundreds of them.
We present $3$ figures in this section that should help the reader
foster his intuition. First, we display the most used codewords in
the testing set (Figure \ref{fig:codes1}). Then, we use the
 LLE\footnote{implementation: 
\url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}} 
algorithm \cite{Roweis2000} to visualize codewords arranged in
coherent groups (Figure \ref{fig:lle}).

Finally, more related to our particular data, we try to assess how many
sustained patterns are represented in the codebook. We look at
the average variance over time, and we get an estimate of $60\%$ of the
codebook (Figure \ref{fig:code_var}).
